---
format: gfm
default-image-extension: ""
editor_options: 
  chunk_output_type: console
---

# kdry - K's "Don't repeat yourself"-collection

<!-- badges: start -->
```{r}
#| echo: false
#| message: false
#| results: asis

pkg <- desc::desc_get_field("Package")
cat_var <- paste(
  badger::badge_lifecycle(),
  badger::badge_cran_release(pkg = pkg),
  gsub("summary", "worst", badger::badge_cran_checks(pkg = pkg)),
  badger::badge_cran_download(pkg = pkg, type = "grand-total", color = "blue"),
  badger::badge_cran_download(pkg = pkg, type = "last-month", color = "blue"),
  gsub("netlify\\.com", "netlify.app", badger::badge_dependencies(pkg = pkg)),
  badger::badge_github_actions(action = utils::URLencode("R CMD Check via {tic}")),
  badger::badge_github_actions(action = "lint"),
  badger::badge_github_actions(action = "test-coverage"),
  badger::badge_codecov(ref = desc::desc_get_urls()),
  sep = "\n"
)
cat_var |> cat()
```
<!-- badges: end -->

This R package provides a collection of helper functions and code snippets to avoid redundancy in the spirit of the *"Don't repeat yourself"* software development principle.

| prefix | description |
| ------ | ----------- |
| -      | No prefix for very basic helper functions |
| dtr_   | Data transform helper functions |
| mlh_   | Machine learning helper functions |
| pch_   | Parallel computing helper functions |
| misc_  | Miscellaneous functions |
| plt_   | Plots|
| rep_   | Reporting helper functions |
| sts_   | Statistical helper functions |

## Installation

To install from CRAN:

```{r}
#| eval: false
install.packages("kdry")
```

You can install the development version of `kdry` with:

```{r}
#| eval: false
install.packages("remotes")
remotes::install_github("kapsner/kdry")
```
